---
title: "R Notebook"
output: html_notebook
---
```{r}
install.packages("tidyverse")
```

```{r}
library(tidyverse)
```
#Print the data set
```{r}
results
```
#Filter the data for the FIFA World Cup in 2018
```{r}
WorldCup2018 <- filter(results, tournament == "FIFA World Cup", country == "Russia")
WorldCup2018
```
# Question 1: What average of goals did the home team make in games won?

## Filter the data with wins of the home team
```{r}
homeTeamWins <- filter(WorldCup2018, home_score > away_score)
homeTeamWins
```
##Get the mean, median and range of home score
```{r}
summary(homeTeamWins)
```
##Histogram 1
```{r}
ggplot(data = homeTeamWins) + geom_histogram(mapping = aes(x = home_score, fill = home_team), color = "black",bins = 15) + labs(title = "Home Team Wins Number of Goals", subtitle = "FIFA World Cup 2018", x = "Number of Goals", y = "Repeated Score", caption = "Kaggle Data Set")
```

#Question 2: What average of goals did the away team make in games won?

## Filter the data with wins of the away team
```{r}
awayTeamWins <- filter(last10Years, home_score < away_score)
awayTeamWins
```
##Get the mean, median and range of away score
```{r}
summary(awayTeamWins)
```

##Histogram 2
```{r}
 ggplot(data = awayTeamWins) + geom_histogram(mapping = aes(x = away_score, fill = away_team), color = "black",bins = 15) + labs(title = "Away Team Wins Number of Goals", subtitle = "FIFA World Cup 2018", x = "Number of Goals", y = "Repeated Score", caption = "Kaggle Data Set")
```
#Question 3: What is the average goal difference of the home team wins?

## Add a variable called difference of goals
```{r}
GoalDifferenceHome<- mutate(homeTeamWins, goal_difference = home_score - away_score)
GoalDifferenceHome
```
##Get the mean, median and range of goal difference
```{r}
summary(GoalDifferenceHome)
```

##Histogram 3
```{r}
ggplot(data = GoalDifferenceHome) + geom_histogram(mapping = aes(x = goal_difference, fill = home_team), color = "black",bins = 15) + labs(title = "Away Team Wins Number of Goals", subtitle = "FIFA World Cup 2018", x = "Difference of Goals", y = "Repeated Difference", caption = "Kaggle Data Set")
```



